---
title: 'Dataset: Biodiversity change'
author: "Owen Petchey"
date: "2/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The publication

From the paper *Global meta-analysis reveals no net change in local-scale plant biodiversity over time* by Vellend et al, 2013, in PNAS [paper on PNAS website](http://www.pnas.org/content/110/48/19456).

## Getting the raw data

[The dataset is available in an Excel file on the PNAS web site.](http://www.pnas.org/content/110/48/19456/tab-figures-data). This excel file (named `sd01.xls) contains to worksheets. One is the data, the other (named metadata) describes the variables.

## Some initial processing

The data worksheet was saved as a csv file `biodiversity_change_vellend_etal_2013_raw.csv`.

## Location on github



```{r}
library(readr)
dd <- read_csv("https://raw.githubusercontent.com/opetchey/insights_public_resources/master/datasets/biodiversity_change_vellend_etal_2013_raw.csv?token=ADEO-h8ObVCL8lx_OMjP19m4HoLVWf-lks5alq-iwA%3D%3D")
```

