---
title: 'Dataset: Hunting to extinction'
author: "Owen Petchey"
date: "2/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The publication

From the paper *Hunting to extinction: biology and regional economy influence extinction risk and the impact of hunting in artiodactyls* by Price and Gittleman, 2007, in PRSB [paper on PRSB website](http://rspb.royalsocietypublishing.org/content/274/1620/1845).

## Getting the raw data

[The dataset is available in an Excel file from Dryad.](https://datadryad.org/resource/doi:10.5061/dryad.82/1). This excel file (named `PriceGittleman_2007_append.xls`) contains one worksheet with data.

## Some initial processing

The data worksheet was saved as a csv file `hunting_to_extinction_price_gittleman_2007_raw.csv`.

The first two rows of the data contain the variable names, so we do a little processing in R, to make one row of variable names and save the new file to csv with `processed1` at the end of the filename, and put it on github.

```{r, eval=FALSE}
library(readr)
library(stringr)
dd <-read_csv("https://raw.githubusercontent.com/opetchey/insights_public_resources/master/datasets/hunting_to_extinction_price_gittleman_2007_raw.csv?token=ADEO-rAmuoLWWvuH2lZVSzSyTNI1cP1_ks5alvr6wA%3D%3D",
              skip=2,
              col_names = FALSE)
hl <- read_lines("https://raw.githubusercontent.com/opetchey/insights_public_resources/master/datasets/hunting_to_extinction_price_gittleman_2007_raw.csv?token=ADEO-rAmuoLWWvuH2lZVSzSyTNI1cP1_ks5alvr6wA%3D%3D", n_max = 2)
hl <- str_split(hl,',')
colnames(dd) <- sub('_$','',paste(hl[[1]],hl[[2]],sep=""))
dd
write_csv(dd, "hunting_to_extinction_price_gittleman_2007_processed1.csv")
```


## Location on github

Here the csv with single header row -- `hunting_to_extinction_price_gittleman_2007_processed1.csv`

```{r}
library(readr)
dd <- read_csv("https://raw.githubusercontent.com/opetchey/insights_public_resources/master/datasets/hunting_to_extinction_price_gittleman_2007_processed1.csv?token=ADEO-i1qB7dKJ5IRK3PPiDfmLKqocBv6ks5alvzVwA%3D%3D")
dd
```

