---
title: "Example of fitting a food web model to data."
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(rdryad)
library(janitor)
library(tidyverse)
library(here)

source("https://raw.githubusercontent.com/opetchey/dumping_ground/master/ADBM_shiny/Plot.matrix.r")
source(here("r/ADBM.functions.r"))
```

# Introduction

This report shows how the allometric diet breadth model of [Petchey et al (2008)](https://www.pnas.org/content/105/11/4191) was fit to empirical food web data. The report is basic and unrefined (purely functional in purpose).

Note that in the [supplementary information](https://www.pnas.org/content/pnas/suppl/2008/03/07/0710672105.DC1/10672SuppAppendix.pdf) Table S4 of Petchey et al (2008), the last names of the food webs in the last two rows are swapped: the values in the last row are for the Ythan food web.

# Empirical data

## 2008 Ythan data

This is the dataset used in Petchey et al (2008). Owen, who was responsible for data management and processing, does not have a record of how this dataset was created.

```{r}
ythan2008.all.web.info <- readRDS(here("data/2008_empirical_data/Ythan.web.2008.RDS"))
Plot.matrix(ythan2008.all.web.info$predation.matrix)
box()
```

## Ythan data from Cirtwill & Eklöf (2020)

Here a version of the [Ythan dataset on Dryad](https://doi.org/10.5061/dryad.1mv20r6) (from [Cirtwill & Eklöf 2020](https://onlinelibrary.wiley.com/doi/10.1111/ele.12955)) is downloaded and then made ready. Code is hidden as there is quite a lot of uninteresting manipulation. The food web is somewhat different from that used in Petchey et al (2008).

```{r echo = FALSE, warning = FALSE}
doi_cirtwill_eklof <- "10.5061/dryad.1mv20r6"
dd <- dryad_download(doi_cirtwill_eklof)
temp = dd$`10.5061/dryad.1mv20r6`[grep(pattern="*.csv", dd$`10.5061/dryad.1mv20r6`)]
all_species_data = read.csv2(temp[1])
this_network1 <- "ythanjacob"
if(this_network1 == "ythanjacob") this_network2 <- "ythan_spnames.csv"

## WARNING: this code assumes the supplied food web matrix has columns and rows
## sorted in the same order

## WARNING: some of the cleaning of species names was only designed for one food web (Ythan)

fw <- read.csv(temp[grep(this_network2, temp)]) %>%
  clean_names() %>%
  select(-1)
rownames(fw) <- colnames(fw)
sp <- all_species_data %>%
  filter(Network == this_network1) %>%
  mutate(sp_names = tolower(Species),
         sp_names = str_replace_all(sp_names, " ", "_"),
         sp_names = str_replace_all(sp_names, "\\.", ""),
         sp_names = str_replace_all(sp_names, "\\(", ""),
         sp_names = str_replace_all(sp_names, "\\)", ""),
         sp_names = str_replace_all(sp_names, "/", "_"),
         BodyWeight = parse_double(BodyWeight))


## Arrange the species by body mass and remove NULLs
sp <- sp %>%
  arrange(BodyWeight) %>%
  filter(BodyWeight != "NULL")

## Species in the food web matrix but not in the species data
#rownames(fw)[!(rownames(fw) %in%  sp$sp_names)]

## Species in the food web matrix but not in the species data
#sp$sp_names[!(sp$sp_names %in%  rownames(fw))]

## Remove species from the food web that are not in the species data
fw <- fw[(rownames(fw) %in%  sp$sp_names),(rownames(fw) %in%  sp$sp_names)]

## Order food web by body weight
fw <- fw[sp$sp_names, sp$sp_names]

## Arrange data for fitting
ythandryad.all.web.info <- list()
ythandryad.all.web.info$predation.matrix <- fw
ythandryad.all.web.info$species.sizes <- sp$BodyWeight

Plot.matrix(ythandryad.all.web.info$predation.matrix)
box()
```


# Fitting the model

## Starting parameter values

The search algorithm can get stuck in local optima, so the search is started multiple times each from a different location in parameter space. Those starting parameter values are loaded from a text file:

```{r}
ratio_initial_pars <- read.csv(here("pars/ratio.initial.pars.txt"),
                               header = FALSE)
```


## Fit model to 2008 Ythan data

Here the outcome is the same as in Petchey et al (2008).

```{r eval = FALSE}
NM.RH.web_2008 <- NM.ratio(ythan2008.all.web.info, ratio_initial_pars)
```

```{r eval = FALSE, echo = FALSE}
saveRDS(NM.RH.web_2008, file=here(paste0("data/",
                                         this_network1, "NMRHweb_2008.RDS")))
```

```{r echo = FALSE}
NM.RH.web_2008 <- readRDS(file=here(paste0("data/",
                                           this_network1, "NMRHweb_2008.RDS")))
```

```{r}
Plot.matrix(NM.RH.web_2008$web)
box()
NM.RH.web_2008$power
NM.RH.web_2008$pars
sum(NM.RH.web_2008$web)
sum(ythan2008.all.web.info$predation.matrix)
```



## Fit model to dryad Ythan data

```{r eval = FALSE}
NM.RH.web_dryad <- NM.ratio(ythandryad.all.web.info, ratio_initial_pars)
```


```{r eval = FALSE, echo = FALSE}
saveRDS(NM.RH.web_dryad,
        file=here(paste0("data/", this_network1, "NMRHweb_dryad.RDS")))
```

```{r echo = FALSE}
NM.RH.web_dryad <- readRDS(file=here(paste0("data/",
                                            this_network1, "NMRHweb_dryad.RDS")))
```


```{r}
Plot.matrix(NM.RH.web_dryad$web)
box()
NM.RH.web_dryad$power
NM.RH.web_dryad$pars
sum(NM.RH.web_dryad$web)
sum(ythandryad.all.web.info$predation.matrix)
```




# Using 2008 parameter estimates

Using the 2008 parameter estimates gives the same results as in Petchey et al (2008).

```{r}
a_2008 <- 1.8e-17
ai_2008 <- -1.98
aj_2008 <- 2.19
b_2008 <- 3.22e-4

EHL_2008 <- Ratio.allometric.EHL(M = ythan2008.all.web.info$species.sizes,
                           e = 1,
                           r.a = 1, r.b = b_2008,
                           a = a_2008, ai = ai_2008, aj = aj_2008,
                           n = 1, ni=-3/4)
web_2008 <- Get.web(EHL_2008)
Plot.matrix(web_2008)
box()
Compare.links(web_2008, ythan2008.all.web.info$predation.matrix)
```

